% William Grimes CV
% URL: https://github.com/williamgrimes/curriculum_vitae


\documentclass[margin,line]{resume}

\usepackage{CJKutf8}
\usepackage{tabularx, multirow}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{marvosym} % contact symbols
\usepackage{pifont}
\usepackage{charter}

\begin{document}

\name{\Huge \sc{William Grimes}\vspace{2mm}}
{
    \hfill                                                           \ \Mobilefone     \vspace{0mm}\\\vspace{0mm}%
    %\hfill ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\ \vspace{0mm}\\\vspace{0mm}% redatct phone number
    \hfill \href{mailto:williamgrimes@gmx.com}{williamgrimes@gmx.com} \ \Letter        \vspace{0mm}\\\vspace{0mm}%
    \hfill \url{http://williamgrimes.xyz/}                        \ \ComputerMouse \vspace{0mm}\\\vspace{-10mm}%
}

\begin{resume}

    %\vspace{-3mm}

    %__________________________________________________________________________________________________________________
    % Summary
    \section{\mysidestyle \textbf{\large{S}\small{UMMARY}}}

    \textbf{Data Engineer} focused on applying machine learning to image and geospatial data. Passionate about software development, maintainability, and applying technology for positive social outcomes.
    %\vspace{-1mm}

\sectionline
    %__________________________________________________________________________________________________________________
    % Skills / Keywords
    \section{\mysidestyle \textbf{\large{S}\small{KILLS}}}

    Python, \hspace{2mm}Java, \hspace{2mm}SQL, \hspace{2mm}R, \hspace{2mm}HTML, \hspace{2mm}CSS, \hspace{2mm}Matlab, \hspace{2mm}Clojure \\
    % regression, decision trees, ensembles, SVM, neural networks, deep learning \\
    NumPy, \hspace{2mm}pandas, \hspace{2mm}GeoPandas, \hspace{2mm}SciPy, \hspace{2mm}scikit-learn, \hspace{2mm}scikit-image, \hspace{2mm}OpenCV, \hspace{2mm}PyTorch, \ldots \\
    % matplotlib, bokeh, plotly, ggplot, Tableau \\
    %MySQL, PostgreSQL, MS SQL Server\\
    %Javascript, HTML, CSS, Semantic UI, Jekyll \\
    Git, \hspace{2mm}Docker, \hspace{2mm}Jenkins, \hspace{2mm}Kafka, \hspace{2mm}Redis, \hspace{2mm}Jupyter, \hspace{2mm}\LaTeX, \hspace{2mm}UNIX, \hspace{2mm}(AWS \& Azure \& GCP)

\sectionline
    %__________________________________________________________________________________________________________________
    % Experience
    \section{\mysidestyle \textbf{\large{E}\small{XPERIENCE}}}

    \textbf{\listing Numerico Technologies}, Amsterdam / Remote \vspace{2mm}\\\vspace{1mm}%
    \textsl{Data Engineer} \hfill \textbf{Feb 2018 -- Ongoing}
    \begin{list2}
        \item Developed software from initial research to national roll-out to optimise traffic inspector deployments on Dutch highways, reducing average time to attend incidents by 45 \%.
        \item Led data science research projects on the use of camera data to monitor traffic flow and speed, and analysis of accident blackspots on highways.
        \item Developed an emergency vehicle routing and travel time engine using GPS trace data.
        \item Responsible for maintaining cloud infrastructure and developing a CI/CD deployment pipeline using Docker Compose and Jenkins.
    \end{list2}

    \textbf{\listing Data Science for Social Good}, Lisbon \vspace{2mm}\\\vspace{1mm}%
    \textsl{Data Scientist / Technical Mentor} \hfill \textbf{Jun 2017 -- Jan 2018}
    \begin{list2}
        \item Developed an open-source fishing risk web application using RShiny, combining vessel tracking data with satellite imagery, using random forest to score vessels according to likelihood of illegal fishing behaviours.
        \item Created a model for predicting road accidents in the Netherlands using a bouquet of classifiers (XGBoost, random forest, SVM) with road features, weather features, and temporal features.
        %\item Learning car accidents occurrence probability on the Dutch highways using transport, weather and road data.
        \item Established AWS EC2 and PostgreSQL infrastructure for several teams, whilst mentoring a team of four, giving them technical advice and performing code reviews.
    \end{list2}

    \textbf{\listing Faculty}, London \vspace{2mm}\\\vspace{1mm}%
    \textsl{Data Science Consultant} \hfill \textbf{Jan 2017 -- Apr 2017}
    \begin{list2}
        %\item Fellowship programme in commercial data science for researchers with strong analytic background.
        \item Consulted with the London Fire Brigade, implementing topic modelling methods to classify a corpus of 37,000 fire incident reports, which revealed previously unknown fire scenarios.
        \item Finished intensive eight week training in machine learning, databases, and statistics.
    \end{list2}

    %\textbf{\listing Laboratory for Molecular Cell Biology (LMCB)} \vspace{2mm}\\\vspace{1mm}%
    %\textsl{PhD Student} \hfill \textbf{Sep 2013 -- Nov 2016}
    %\begin{list2}
    %    \item Joint scholarship at LMCB and A*STAR Bioinformatics Institute, Singapore.
    %	\item Developed automated image analysis pipelines for use in high-throughput microscopy assays, using machine learning to classify cell organelles.
    %	%\item Published articles in \emph{Nature Scientific Reports} and \emph{Journal of Thrombosis and Haemostasis}.
    %\end{list2}

    \textbf{\listing National Institute of Informatics(\begin{CJK}{UTF8}{min}国立情報学研究所\end{CJK})}, Tokyo \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{Jun 2013 -- Sep 2013}
    \begin{list2}
      \item Wrote software in Java for annotation and classification of phenotypes in $\mu$CT images of mice.
    \end{list2}

\sectionline
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \vspace{1mm}

    \textbf{\listing PhD Bioinformatics} \vspace{2mm}\\\vspace{1mm}%
    \textsl{University College London and A*STAR Singapore} \hfill \textbf{Sep 2013 -- Nov 2016}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Thesis: \emph{Image processing and analysis methods in quantitative endothelial cell biology}
	\item Developed automated image analysis pipelines for use in high-throughput microscopy assays, using machine learning to segment and classify cell organelles.
    \end{list2}\vspace{-1.5mm}

    \textbf{\listing MSc Computer Science} \vspace{2mm}\\\vspace{1mm}%
    \textsl{University College London} \hfill \textbf{Sep 2012 -- Sep 2013}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Awarded Aardvark Scholarship 2012
    \end{list2}\vspace{-1.5mm}

    \textbf{\listing BSc Natural Sciences} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Durham University} \hfill \textbf{Sep 2009 -- Sep 2012}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Second Class (Division One) Honours - Physics and Geophysics
    \end{list2}\vspace{-1.5mm}

    \vspace{-1mm}

\sectionline
    %__________________________________________________________________________________________________________________
    % Extra
    \section{\mysidestyle \textbf{\large{H}\small{OBBIES}}}

    In my free time I enjoy cycling, cross-country skiing, learning French, Vipassana meditation, playing chess, and exploring the Ethereum ecosystem.


\end{resume}
\end{document}
